%%
%% This is file `cvtest.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% currvita.dtx  (with options: `testfile')
%% 
%% LaTeX sample file for the currvita package
%% 
%% Copyright (C) 1999 Axel Reichert
%% See the files README and COPYING.
%% 
%% \CharacterTable
%%   {Upper-case    \A\B\C\D\E\F\G\H\I\J\K\L\M\N\O\P\Q\R\S\T\U\V\W\X\Y\Z
%%   Lower-case    \a\b\c\d\e\f\g\h\i\j\k\l\m\n\o\p\q\r\s\t\u\v\w\x\y\z
%%   Digits        \0\1\2\3\4\5\6\7\8\9
%%   Exclamation   \!     Double quote  \"     Hash (number) \#
%%   Dollar        \$     Percent       \%     Ampersand     \&
%%   Acute accent  \'     Left paren    \(     Right paren   \)
%%   Asterisk      \*     Plus          \+     Comma         \,
%%   Minus         \-     Point         \.     Solidus       \/
%%   Colon         \:     Semicolon     \;     Less than     \<
%%   Equals        \=     Greater than  \>     Question mark \?
%%   Commercial at \@     Left bracket  \[     Backslash     \\
%%   Right bracket \]     Circumflex    \^     Underscore    \_
%%   Grave accent  \`     Left brace    \{     Vertical bar  \|
%%   Right brace   \}     Tilde         \~}
\documentclass[12pt,a4paper]{article}
\usepackage[german]{babel}
\usepackage[usenames, dvipsnames]{color}
\usepackage[none]{hyphenat}
\usepackage{hyperref}

\definecolor{mygray}{gray}{0.9}

\usepackage{currvita}
\newcommand*{\ac}[1]{\mbox{#1}}
\tolerance=600
\begin{document}
\begin{cv}{Curriculum Vitae}
  \begin{cvlist}{}
  \item \colorbox{mygray} {Giacomo Vagni}\\
  \emph{PhD Student in Sociology \textcolor{Gray}{(DPhil)}}
  
    \textcolor{Orange} {Centre for Time Use Research} \\
     Department of Sociology, \textcolor{Blue}{University of Oxford} 
    \item Nuffield College \\ 
    1 New Rd, Oxford OX1 1NF, United Kingdom
  \item Tel.:~(0044)~1865\,284464\\
    E"~Mail:~\href{mailto:giacomo.vagni@sociology.ox.ac.uk}{giacomo.vagni@sociology.ox.ac.uk}
    \item http://www.timeuse.org/team/Vagni \\
  \end{cvlist}
  
  \begin{cvlist}{Research Interests}
  \item[] Time Use. Families. Stratification. \\  Sequence Analysis. Computational Social Science. \\ High Performance Computing. 
  \end{cvlist}
  
  \begin{cvlist}{Education}
  \item[2015--current] DPhil Student in Sociology. \\ University of Oxford. Nuffield College. 
  \item[2012-2014] MA in Sociology. University of Geneva. 
  \item[2014] Boston University (Exchange program). 
  \item[2008-2011] BA in Sociology \& Anthropology. \\ Universit{\'e} Libre de Bruxelles. 
  \end{cvlist}
 
  
  \begin{cvlist}{Publications}
  \footnotesize
  	
  \item [2016] Bolzman, C., \& Vagni, G. (2016). Forms of care among native Swiss and older migrants from Southern Europe: a comparison. \emph{Journal of Ethnic and Migration Studies}, 43(2), 250-269.
  	  
  \item [2015]
  Bolzman, C., \& Vagni, G. (2015). ‪ {\'E}galit{\'e} des chances? Une
  comparaison des conditions de vie des personnes {\^a}g{\'e}es immigr{\'e}es
  et ``nationales''. \emph{Hommes \& Migrations}, 1309, 19-28.
  \end{cvlist}
  
  \begin{cvlist}{\ac{Expertise}}
  \item[Languages] R (\emph{expert}), Rcpp, Python (\emph{intermediate}),  C++ (\emph{beginner}) 
  \item[Tools] RStudio, Shiny, \ac{WEKA}, Ucinet, NetLogo, \ac{SPSS} \\ \LaTeX, Word, Excel, InDesign, \ac{VIM} \\ 
 \ac{HTML},  MySQL,  Github \\ 
 Experience in using ARCUS (Oxford Supercomputing facilities)
  \end{cvlist}

 \begin{cvlist}{Conference Papers}
 	
 	\item [2016] \emph{Inequality and Family Time}. Time Use Survey Methodical Workshop.  Tampere, Finland. 
 		
 	\item [] \emph{Family Time and Stratification}. Inequality Research Group. Department of Social Policy, University of Oxford. 
 		
 	\item [] \emph{The Causal Effect of Spouse on Enjoyment}. International Association of Time Use Research Conference 2016. Seoul, South Korea.  
 	
 	\item [] \emph{Modelling Activity Sequences}. NCRM Research Methods Festival 2018. Session: Time Use Diary Data: Methodological Innovations. University of Bath, UK. 
 		
 	\item [] \emph{The Causal Effect of Spouse on Enjoyment}. Graduate Research Seminar. Nuffield College, University of Oxford, UK. 
 		
 	\item [2015] \emph{Sharing daylight. Conjugal-parental-family time in Switzerland.}. European Sociological Association Conference. Prague, Czech.  
 	
 	\item [] \emph{Exploring the Reliability of Co-Presence Data in the UK 2000 Time Use Survey}. International Association of Time Use Research Conference 2015. Ankara, Turkey. 
 	
 	\item [2014] \emph{With whom do Swiss couples spend their Saturday?}. International Association of Time Use Research Conference 2014. Turku, Finland.
 	
 	\item [2013] \emph{L'usage du temps conjugal. Analyse de sequences des reseaux de couple un samedi de conge.}. Research Seminar in Statistics for Social and Population Sciences. University of Geneva. Switzerland. 
 
 	
 \end{cvlist}


  \cvplace{Oxford}
  \date{~January~2017}
\end{cv}
\end{document}
\endinput
%%
%% End of file `cvtest.tex'.
