
\documentclass[12pt,a4paper]{article}
\usepackage[german]{babel}
\usepackage[usenames, dvipsnames]{color}
\usepackage[none]{hyphenat}
\usepackage{hyperref}

\definecolor{mygray}{gray}{0.9}

\usepackage{currvita}
\newcommand*{\ac}[1]{\mbox{#1}}
\tolerance=600
\begin{document}
\begin{cv}{Curriculum Vitae}
  \begin{cvlist}{}
  \item \textbf{Giacomo Vagni}, PhD\\
  \emph{Research Fellow}
   
   \item Centre for Time Use Research \\
    UCL Institute of Education, University College London
  %  \item Nuffield College \\ 
    20 Bedford Way, London WC1H 0AL, United Kingdom
  \item Tel.:~(0044)~1865\,284464\\
    E"~Mail:~\href{mailto:giacomo.vagni@sociology.ox.ac.uk}{giacomo.vagni@sociology.ox.ac.uk} \\ 
    \href{https://giacomovagni.com} {https://giacomovagni.com} \\
   \end{cvlist}
  
  \begin{cvlist}{Research Interests}
  \item[] Time Use. Families. Social Stratification. \\  Sequence Analysis. Causality. 
  \end{cvlist}
  
  \begin{cvlist}{Education}
  \item[2015--2020] DPhil (PhD) in Sociology. \\ University of Oxford. Nuffield College. UK. \\ \emph{Thesis title}: ``In Search of Lost Time Patterns. How Class, Gender and Social Contexts Structure our Daily Lives.'' Examiners: Christiaan Monden and Laurent Lesnard. Supervisors: Oriel Sullivan and Jonathan Gershuny.
  
  \item[2012-2014] MA in Sociology. University of Geneva. CH. 
  \item[2008-2011] BA in Sociology \& Anthropology. \\ Universit{\'e} Libre de Bruxelles. Belgium. 
  \end{cvlist}
  
      \begin{cvlist}{Visiting}
      	\item[2017 (Aug-Dec)] Cornell University, Department of Sociology. USA 
      	\item[2017 (April)] National Institute for Demographic Studies (INED), France. 
      	\item[2014] Boston University, Department of Sociology. USA
      \end{cvlist}
      
 
 \newpage
 
   \begin{cvlist}{Publications}	
   	
	\item [2020] \textbf{Vagni, G.} (Forthcoming). ``The Social Stratification of Time Use Patterns.'' \emph{British Journal of Sociology}. 
	
	 \item [2019] \textbf{Vagni, G.} (2019). ``Alone Together: Gender Inequalities in Couple Time.'' \emph{Social Indicators Research.} 1-23. \href{https://doi.org/10.1007/s11205-019-02135-7}{doi: 10.1007/s11205-019-02135-7} 
	 
		\item [] \textbf{Vagni, G.}  (2019). ``Family Time Together.'' In J. Gershuny and O. Sullivan (Eds.) \emph{What We Really Do All Day} (pp. 220-265). London:Penguin Books.  
		
		
		 \item [2018] \textbf{Vagni, G.} \& Cornwell, B. (2018). ``Patterns of everyday activities across social contexts.'' \emph{Proceedings of the National Academy of Sciences.} 115(24), 6183-6188. \\ \href{https://doi.org/10.1073/pnas.1718020115}{doi: 10.1073/pnas.1718020115} 
		 		  	
		  		    	 	 
		   \item [] Bolzman, C., \& \textbf{Vagni, G.} (2018). ``And we are still here: Life courses and life conditions of Italian, Spanish and Portuguese retirees in Switzerland.'' In I. Vlase and B. Voicu (Eds.) \emph{Gender, Family, and Adaptation of Migrants in Europe.} (pp. 75-97). London:Palgrave Macmillan. \href{https://doi.org/10.1007/978-3-319-76657-7_4}{doi: 10.1007/978-3-319-76657-74} 
  	 	    	 
   	\item [2016] Bolzman, C., \& \textbf{Vagni, G.}  (2016). ``Forms of care among native Swiss and older migrants from Southern Europe: a comparison.'' \emph{Journal of Ethnic and Migration Studies}, 43(2), 250-269. 
   	\href{https://doi.org/10.1080/1369183X.2016.1238908}{doi: 10.1080/1369183X.2016.1238908} 
   	
   	\item [2015]
   	Bolzman, C., \& \textbf{Vagni, G.}(2015). ``{\'E}galit{\'e} des chances? Une
   	comparaison des conditions de vie des personnes {\^a}g{\'e}es immigr{\'e}es
   	et nationales.'' \emph{Hommes \& Migrations}, 1309, 19-28.
   				  
   \end{cvlist}
 
 \begin{cvlist}{Under Review}
 
   \item Vagni, G.``All You Need is Love. Searching for Causal Effects of Spouse on Enjoyment.'' 	
 	\item Vagni, G. ``From Constraints to Culture. The Social Stratification of Parental Time.'' 
 	\item Vagni, G., and Widmer, E. ``Couple Time and Partnership Quality: an Empirical Assessment using Diary Data."
 \end{cvlist}
 
 \begin{cvlist}{Working Papers}

  	\item ``The Motherhood Earnings Penalty: A New Approach and New
  	Estimates for the UK.'' (with Richard Breen)
  	\item ``Schedules, Resources, and the Division of Household Labour: A Latent Class Approach.'' (with Oriel Sullivan)
  	\item ``Couple Work-schedules and the Division of Labor.'' (with Oriel Sullivan)
  	\item ``Bring It All Back Home. Decomposing the Stratification of Childcare Over Time.''

\end{cvlist}
 
  
  \begin{cvlist}{Awards}
  	\item[2019-2020]  Early Postdoc.Mobility (Swiss National Science Foundation)
  	\item[2018-2019]  Doc.Mobility (Swiss National Science Foundation)
  	\item[2017]  Brettschneider Exchange Fund (Cornell University)
  	\item [2015-2018] ERC Scholarship. University of Oxford. 
  	\item [2016]  Best Student Paper Award (Bronze). 38th International Association for Time Use Research. Seoul, Korea, July 22, 2016. 
  	\item [2014] Prize of Best Master Thesis - Sociology.  University of Geneva. 
  \end{cvlist}
  
\begin{cvlist}{Affiliations and Academic Memberships}
	\item[Affiliate] \textbf{Associate Member.} Nuffield College. Oxford. 
	\item[Member] European Sociological Association (ESA); International Sociological Association (ISA); RC-28; The Royal Statistical Society (RSS); International Association of Time Use Research (IATUR); 
	British Society for Population Studies (BSPS). 
\end{cvlist}

\begin{cvlist}{\ac{Expertise}}
	\item[Languages] R (\emph{expert}), Rcpp, Python (\emph{intermediate}),  C++ (\emph{beginner}) 
	
	\item[Statistics] Sequence Analysis (\emph{advanced}), 
	Clustering Analysis (\emph{intermediate}), 
	Ordinary Least Squares (\emph{intermediate}), Structural Equations Modelling (\emph{intermediate}), Multiple Correspondence Analysis (\emph{intermediate}), 
	Network Analysis (\emph{intermediate/beginner})
	
	\item[Tools] RStudio, Shiny, \ac{WEKA}, Ucinet, NetLogo, \ac{SPSS} \\ \LaTeX, Word, Excel, InDesign, \ac{VIM} \\ 
	\ac{HTML}, MySQL, Github.
\end{cvlist}

  \cvplace{Oxford}
  \date{~March~2020}
\end{cv}
\end{document}
\endinput
%%
%% End of file `cvtest.tex'.
