

\documentclass[12pt,a4paper]{article}
\usepackage[german]{babel}
\usepackage[usenames, dvipsnames]{color}
\usepackage[none]{hyphenat}
\usepackage{hyperref}

\definecolor{mygray}{gray}{0.9}

\usepackage{currvita}
\newcommand*{\ac}[1]{\mbox{#1}}
\tolerance=600
\begin{document}
	\begin{cv}{Courses Assisted (statistcs \& CS)}

		\begin{cvlist}{}
			
			\item[2017] Summer School in Advanced
			Quantitative Methods (Structural Equations Modelling). Department of Education. University of Oxford. 
				
			\item[] Linux. A comprehensive introduction for researchers. IT department. University of Oxford. 
			
			\item[] C++. A comprehensive introduction. IT department. University of Oxford
				
			\item[2016] Advances in Causal Inference. \emph{Prof Elias Dinas}. DPIR. University of Oxford
					
			\item[] Causality. \emph{Prof Richard Breen}. Department of Sociology. University of Oxford
								
			\item[2015] Introduction to
			Computer Science I (Python). \emph{Prof David G. Sullivan}. Department of Computer Science. Boston University. 
					
			\item[] Sequence Analysis. \emph{Prof Gilbert Ritschard}. Department of Sociology. Universtiy of Geneva
			
			\item[] Statistical Analysis of Categorical Data. \emph{Prof Gilbert Ritschard}. Department of Sociology. Universtiy of Geneva
			
			\item[] Item Nonresponse and Multiple Imputation. \emph{Prof Susanne R{a}ssler} GESIS summer school. 
			
			\item[] Longitudinal Data and Survival Models. \emph{Prof Andr{\'e} Berchtold.} Department of Sociology. Universtiy of Geneva. 		
											
		\end{cvlist} 

  \cvplace{Giacomo Vagni}
  \date{~June~2017}
\end{cv}
\end{document}
\endinput
%%
%% End of file `cvtest.tex'.
