
\documentclass[12pt,a4paper]{article}
\usepackage[german]{babel}
\usepackage[usenames, dvipsnames]{color}
\usepackage[none]{hyphenat}
\usepackage{hyperref}

\definecolor{mygray}{gray}{0.9}

\usepackage{charter}

\usepackage{currvita}
\newcommand*{\ac}[1]{\mbox{#1}}
\tolerance=600
\begin{document}
\begin{cv}{Curriculum Vitae}
  \begin{cvlist}{}
  \item \colorbox{mygray} { \textbf{Giacomo Ecce Vagni}  }

	\item  Departement of Sociology, University of Oxford  \\ Nuffield College, 1 New Rd, Oxford OX1 1NF, UK

      \item 
      \href{http://accountablepictures.com} {accountablepictures.com} \\ 
     \href{https://giacomovagni.com} {giacomovagni.com} \\
    % E"~Mail:~\href{giacomovagni@gmail.com}{giacomovagni@gmail.com} \\
    
  \end{cvlist}
  
  I am a sociologist and freelance filmmaker based in Oxford.  I have directed several short experimental films and documentaries on very low budget.
  I am interested in social topics such as economic inequality, social mobility, immigration and animal rights.
  
  \hspace{3cm}
  
   \begin{cvlist}{Selected Projects}
   	\footnotesize
   	
   	   	\item[2018] ``Traces of Shadows''. (Short Documentary)
   	   	\\ Writer, director and editor. USA. Runtime: 10min. 
   	   	\\ \colorbox{mygray}{Official Selection}: \textbf{Ethnografilm 2019 (FR)}. 
   	   	
   	\item[2018] ``The Hidden Injuries of Dreams''. (Short Experimental)
   	\\ Writer, director and editor. USA. Runtime: 6min. 
   	\\ \colorbox{mygray}{Official Selection}: \textbf{Aesthetica Short Film Festival 2018 (UK), Nottingham International Film Festival 2018 (UK), Oxford International Film Festival 2018 (UK)}. 
    \\ \colorbox{mygray}{Awards}: Best Experimental Film Oxford International Film Festival, Best Experimental Film Nottingham International Film Festival.
   	 			   	   		   	   	
   \end{cvlist}
   
        
        \begin{cvlist}{Education}
        	\item[2015--current] PhD Student in Sociology. \\ University of Oxford. Nuffield College. UK. 
        	\item[2012-2014] MA in Sociology. University of Geneva. CH. 
        	\item[2008-2011] BA in Sociology \& Anthropology. \\ Universit{\'e} Libre de Bruxelles. Belgium. 
        \end{cvlist}
             
        \begin{cvlist}{\ac{Expertise}}
        	\item[Shooting]  Canon EOS C100, Canon 5d.
        	\item[Editing] Adobe Premiere Pro, Final Cut Pro X
        	\item[Misc] InDesign, Adobe Lightroom, \LaTeX, R
        \end{cvlist}
        
         \newpage
     
     \begin{cvlist}{All Film/Video Projects}
     	\footnotesize
     	
     	\item[2018] ``Traces of Shadows''. (Short Documentary)
     	\\ Writer, director and editor. USA. Runtime: 10min. 
      \href{https://vimeo.com/248001217} {link} {\tiny (pass = texas)}

     	\item[2017] ``The Hidden Injuries of Dreams''. (Short Experimental)
     	\\ Writer, director and editor. USA. Runtime: 6min. 
      \href{https://vimeo.com/269840950} {link} {\tiny (pass = hidden)}
     	
     	\item[2016] ``The Weight of Words''. (Short Experimental)
     	\\ Writer, director and editor. UK. Runtime: 5min. 
      \href{https://accountablepictures.tumblr.com/post/163641983960/soundtrack-available-at-more} {link}
     	
     	\item[2016] ``MOVE project''. (With Professor David Kirk, University of Oxford)
     		\\ Director and editor. UK. Runtime: 2min. 
        \href{https://vimeo.com/236493125} {link}
        
     	\item[2015] ``The Gift''. (Short Fiction)
     	\\ Writer, director and editor. Switzerland. Runtime: 10min. 
      \href{https://accountablepictures.tumblr.com/post/163636586925} {link}
     	
     	\item[2015] ``Looking for Bourdieu''. (Short film for Nuffield College student Pantomime, University of Oxford)
     	 \\ Director, actor and editor. UK. Runtime: 8min. 
       \href{https://www.youtube.com/watch?v=i-aHf-_BgKc} {link}
 	     	
     	\item[2014] ``Les 61 Images d'une Avant-Derni\`ere Minute''. (Short Experimental)
     	\\ Writer, director and editor. Switzerland. Runtime: 10min. \emph{Nikon Film Festival}.
     	\href{https://accountablepictures.tumblr.com/post/163635947580/cinema-experimentalfilm-po%C3%A9sie-poetry} {link}

     	\item[2014] ``Nom Propre''. (Short Experimental)
     	\\ Writer, director and editor. Switzerland. Runtime: 10min. 
     	\href{https://accountablepictures.tumblr.com/post/163636007185} {link}
      
     	\item[2011] ``Prol\'egom\`enes au Mouvement	''. (Fiction)
     	\\ Writer, director and editor. Belgium. Runtime: 28min. 
     	
     \end{cvlist}
    
 
   \begin{cvlist}{Publications}
	\footnotesize
	
		\item [2018] \textbf{Vagni, G.}  (Forthcoming). ``Family Time at the turn of the 21st century.'' In J. Gershuny and O. Sullivan (Eds.) \emph{The Great Day} (pp. 220-265). London:Penguin Books.  
		
		\item [] \textbf{Vagni, G.} \& Cornwell, B. (2018). ``Patterns of everyday activities across social contexts.'' \emph{Proceedings of the National Academy of Sciences.} 
  	
   	\item [2016] Bolzman, C., \& \textbf{Vagni, G.}  (2016). ``Forms of care among native Swiss and older migrants from Southern Europe: a comparison.'' \emph{Journal of Ethnic and Migration Studies}, 43(2), 250-269.

   \end{cvlist}
 
  \cvplace{Oxford}
  \date{~December~2018}
    
\end{cv}
\end{document}
\endinput
%%
%% End of file `cvtest.tex'.
