
\documentclass[10pt,a4paper]{article}
\usepackage[german]{babel}
\usepackage[usenames, dvipsnames]{color}
\usepackage[none]{hyphenat}
\usepackage{hyperref}

\definecolor{mygray}{gray}{0.9}

\usepackage{currvita}
\newcommand*{\ac}[1]{\mbox{#1}}
\tolerance=600
\begin{document}
\begin{cv}{Curriculum Vitae}
  \begin{cvlist}{}
  \item \colorbox{mygray} {Giacomo Vagni}\\
  \emph{PhD Student in Sociology \textcolor{Gray}{(DPhil)}}
  
    \textcolor{Orange} {Centre for Time Use Research} \\
     Department of Sociology, \textcolor{Blue}{University of Oxford} 
    \item Nuffield College \\ 
    1 New Rd, Oxford OX1 1NF, United Kingdom
  \item \href{mailto:giacomo.vagni@sociology.ox.ac.uk}{giacomo.vagni@sociology.ox.ac.uk}
    
    \item \href{https://giacomovagni.com} {https://giacomovagni.com} \\
    
  \end{cvlist}
  
  \begin{cvlist}{Research Interests}
  \item[] Time Use. Families. Social Stratification. \\  Sequence Analysis. Computational Social Science.
  \end{cvlist}
  
  \begin{cvlist}{Education}
  \item[2015--current] DPhil Student in Sociology. \\ University of Oxford. Nuffield College. UK. 
  \item[2012-2014] MA in Sociology. University of Geneva. CH. 
  \item[2008-2011] BA in Sociology \& Anthropology. \\ Universit{\'e} Libre de Bruxelles. Belgium. 
  \end{cvlist}
  
 
   \begin{cvlist}{Publications}
	
	\item [2018] Vagni, G. \& Cornwell, B. (forthcoming). ``Patterns of everyday activities across social contexts.'' \emph{Proceedings of the National Academy of Sciences.}
			 
   	 \item [] Vagni, G. (forthcoming). ``Family Time at the turn of the 21st century.'' In J. Gershuny and O. Sullivan (Eds.) \emph{The Great Day} (pp. 220-265). London:Penguin Books.  
   	 
   	 \item [] Bolzman, C., \& Vagni, G. (forthcoming). ``And we are still here: Life courses and life conditions of Italian, Spanish and Portuguese retirees in Switzerland.'' In I. Vlase and B. Voicu (Eds.) \emph{Gender, Family, and Adaptation of Migrants in Europe. A Life Course Perspective} (pp. 75-97). London:Palgrave Macmillan.

   	\item [2016] Bolzman, C., \& Vagni, G. (2016). ``Forms of care among native Swiss and older migrants from Southern Europe: a comparison.'' \emph{Journal of Ethnic and Migration Studies}, 43(2), 250-269.
   	
   	\item [2015]
   	Bolzman, C., \& Vagni, G. (2015). ``{\'E}galit{\'e} des chances? Une
   	comparaison des conditions de vie des personnes {\^a}g{\'e}es immigr{\'e}es
   	et `nationales'.'' \emph{Hommes \& Migrations}, 1309, 19-28.
   \end{cvlist}
 
 \begin{cvlist}{Under Review}
  
      \item Vagni, G. (2017) ``Alone Together: Gender Inequalities in Couple Time''. 
      \item Vagni, G. (2017)  ``From Constraints to Culture. The Social Stratification of Parental Time.'' 
      \item Vagni, G., and Widmer, E. (2017)  ``Time Together and Partnership Quality.'' 

 \end{cvlist}
 

 \begin{cvlist}{Visiting}
 	\item[2017 (Aug-Dec)] Cornell University, Department of Sociology. USA 
 	\item[2017 (April)] National Institute for Demographic Studies (INED), France. 
 	\item[2014] Boston University, Department of Sociology. USA
 \end{cvlist}
 
 
 \begin{cvlist}{Awards}
 	\item[2018]  Doc.Mobility (Swiss National Science Foundation)
 	\item[2017]  Brettschneider Exchange Fund (Cornell University)
 	\item [2015-2018] ERC Scholarship. University of Oxford. 
 	\item [2016]  Best Student Paper Award (Bronze). 38th International Association for Time Use Research. Seoul, Korea, July 22, 2016. 
 	\item [2014] Prize of Best Master Thesis - Sociology.  University of Geneva. 
 \end{cvlist}
 



  \begin{cvlist}{\ac{Expertise}}
  \item[Languages] R (\emph{expert}), Rcpp, Python (\emph{intermediate}),  C++ (\emph{beginner}) 
  
  \item[Statistics] Sequence Analysis (\emph{advanced}), 
  Clustering Analysis (\emph{intermediate}), 
  Ordinary Least Squares (\emph{intermediate}), Structural Equations Modelling (\emph{intermediate}), Multiple Correspondence Analysis (\emph{intermediate}), 
  Network Analysis (\emph{intermediate/beginner})
  
  \item[Tools] RStudio, Shiny, \ac{WEKA}, Ucinet, NetLogo, \ac{SPSS} \\ \LaTeX, Word, Excel, InDesign, \ac{VIM} \\ 
 \ac{HTML},  MySQL,  Github \\ 
 Experience in using ARCUS (Oxford Supercomputing facilities)
  \end{cvlist}



  \cvplace{Oxford}
  \date{~May~2018}
\end{cv}
\end{document}
\endinput
%%
%% End of file `cvtest.tex'.
